*Platynereis dumerilii* three-day-old connectome --- cell-type compendium

### 2024-10-18 supplements/celltype_compendium_website/index.qmd
suppl cell type website: add INs

# catmaid connection
conn_http1 <- catmaid_login(
  server="https://catmaid.jekelylab.ex.ac.uk/", 
  authname="AnonymousUser",
  config=httr::config(ssl_verifypeer=0, http_version=1)
)
```

@@

#### Ciliary photoreceptors

@@

# PU neurons celltype88-98
annot <- ("celltype90")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

# PU neurons celltype88-98
annot <- ("celltype92")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

#### PB (penetrating biciliated) mechanosensory neurons

@@

# PB neurons celltype80 and 54
annot <- ("celltype54")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

### Chemoreceptors

@@

@@

@@

@@

@@

@@

@@

@@

```{r}
#| echo: false
#	SN0DLSO1.2-3
annot <- ("celltype29")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

```{r}
#| echo: false
#	SN0DLSO1.2-1
annot <- ("celltype30")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

@@

@@

@@

@@

@@

>>>>

# catmaid connection
#conn_http1 <- catmaid_login(
#  server="https://catmaid.jekelylab.ex.ac.uk/", 
#  authname="AnonymousUser",
#  config=httr::config(ssl_verifypeer=0, http_version=1)
#)

# catmaid connection, needs username, password AND token - weird!
{
  # can run this separate file using source function
  conn <- source("~/R/conn.R")
  #for larger calls we need to use http/1, see https://www.gitmemory.com/issue/natverse/rcatmaid/158/641537466
  #for this we configure to http/1.1
#  conn_http1 = catmaid_login(conn=conn, config=httr::config(ssl_verifypeer=0, http_version=1))
}
```

@@

#### Ciliary photoreceptors {#sec-cPRC}

@@

# PU neurons celltype88-98
#VentraltrunkPUunp
annot <- ("celltype90")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

# PU neurons celltype88-98
#hPUc1
annot <- ("celltype92")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

#### PB (penetrating biciliated) mechanosensory neurons  {#sec-PB}

@@

# PB neurons celltype80 and 54
#pygPBunp
annot <- ("celltype54")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "ventral")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

#### Flow-sensory MS neurons

# MS neurons celltype35-38
annot <- ("celltype35")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype35.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype35.html){target="_blank"}

# MS neurons celltype35-38
annot <- ("celltype36")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype36.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype36.html){target="_blank"}

# MS neurons celltype35-38
annot <- ("celltype37")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype37.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype37.html){target="_blank"}

# MS neurons celltype35-38
annot <- ("celltype38")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype38.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype38.html){target="_blank"}

#### Chaetal mechanosensory neurons

# chaeMech
annot <- ("celltype71")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype71.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype71.html){target="_blank"}

#### Other putative mechanosensory neurons in the mechanosensory girdle

```{r}
#| echo: false
#SNblunt
annot <- ("celltype148")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype148.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype148.html){target="_blank"}

```{r}
#| echo: false
#SNbronto
annot <- ("celltype168")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype168.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype168.html){target="_blank"}

```{r}
#| echo: false
#SNFVa
annot <- ("celltype143")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype143.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype143.html){target="_blank"}

```{r}
#| echo: false
#SNFVa
annot <- ("celltype143")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype143.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype143.html){target="_blank"}

```{r}
#| echo: false
#SNPDF-pyg
annot <- ("celltype115")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype115.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype115.html){target="_blank"}

```{r}
#| echo: false
#SNpygM
annot <- ("celltype170")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype170.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype170.html){target="_blank"}

### Nuchal organ chemoreceptors

@@

### Mushroom body sensory cells

```{r}
#| echo: false
#SNtrpa
annot <- ("celltype190")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

![](snapshots/celltype190.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype190.html){target="_blank"}

```{r}
#| echo: false
#SNtorii
annot <- ("celltype187")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype187.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype187.html){target="_blank"}

@@

```{r}
#| echo: false
#SN-NS27
annot <- ("celltype137")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

![](snapshots/celltype137.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype137.html){target="_blank"}

```{r}
#| echo: false
#SN-NS19
annot <- ("celltype133")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

![](snapshots/celltype133.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype133.html){target="_blank"}

```{r}
#| echo: false
#SN-NS18
annot <- ("celltype138")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

![](snapshots/celltype138.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype138.html){target="_blank"}

```{r}
#| echo: false
#SN-NS17
annot <- ("celltype131")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

![](snapshots/celltype131.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype131.html){target="_blank"}

```{r}
#| echo: false
#SN-NS1
annot <- ("celltype110")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype110.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype110.html){target="_blank"}

### Apical organ sensory cells

```{r}
#| echo: false
#	SNadNS22
annot <- ("celltype141")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype141.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype141.html){target="_blank"}

```{r}
#| echo: false
#	SN47Ach
annot <- ("celltype52")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype52.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype52.html){target="_blank"}

```{r}
#| echo: false
#	SN-YF5cil
annot <- ("celltype132")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype132.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype132.html){target="_blank"}

```{r}
#| echo: false
#	SN47Ach
annot <- ("celltype52")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype52.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype52.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS6
annot <- ("celltype135")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype135.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype135.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS5
annot <- ("celltype130")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype130.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype130.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS4
annot <- ("celltype112")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype112.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype112.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS3
annot <- ("celltype111")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype111.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype111.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS29
annot <- ("celltype136")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype136.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype136.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS22
annot <- ("celltype129")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype129.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype129.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS20
annot <- ("celltype134")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype134.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype134.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS16
annot <- ("celltype139")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype139.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype139.html){target="_blank"}

```{r}
#| echo: false
#	SN-NS15
annot <- ("celltype113")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype113.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype113.html){target="_blank"}

See also @sec-cPRC for the apical organ ciliary photoreceptors.

### Dorsolateral sensory organ sensory cells

@@

@@

```{r}
#| echo: false
#	SN-DLSO1.3
annot <- ("celltype163")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

![](snapshots/celltype163.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype163.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO1.2-3
annot <- ("celltype29")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

```{r}
#| echo: false
#	SN-DLSO1.2-1
annot <- ("celltype30")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

```{r}
#| echo: false
#	SN-DLSO1.1NP
annot <- ("celltype172")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

@@

![](snapshots/celltype172.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype172.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO1.1
annot <- ("celltype173")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype173.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype173.html){target="_blank"}

```{r}
#| echo: false
#	SN-DLSO1.0
annot <- ("celltype103")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype103.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype103.html){target="_blank"}

@@

```{r}
#| echo: false
#SNasym
annot <- ("celltype51")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype51.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype51.html){target="_blank"}

```{r}
#| echo: false
#SNaanc
annot <- ("celltype114")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype114.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype114.html){target="_blank"}

```{r}
#| echo: false
#SNstiff
annot <- ("celltype167")
plot_cell_name(annot, "Sensory neuron")
plot_cell_chars(annot, "Sensory neuron")
rgl <- plot_cell_rgl(annot, "Sensory neuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype167.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype167.html){target="_blank"}

## Interneurons

### Visual system interneurons

```{r}
#| echo: false
#IN1
annot <- ("celltype2")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()
path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)
```

![](snapshots/celltype2.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype2.html){target="_blank"}

```{r}
#| echo: false
#INton
annot <- ("celltype3")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()
path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)
```

![](snapshots/celltype3.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype3.html){target="_blank"}

```{r}
#| echo: false
#INR1
annot <- ("celltype171")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()
path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)
```

![](snapshots/celltype171.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype171.html){target="_blank"}

### Ciliomotor interneurons

```{r}
#| echo: false
#cMNATO
annot <- ("celltype11")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype11.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype11.html){target="_blank"}

```{r}
#| echo: false
#cMNdc
annot <- ("celltype12")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype12.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype12.html){target="_blank"}

```{r}
#| echo: false
#cMNPDF-vcl1
annot <- ("celltype10")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype10.png){height=200}

[3D visualisation](_site/celltype_RGLs/celltype10.html){target="_blank"}

### Apical organ interneurons

```{r}
#| echo: false
#INNOS
annot <- ("celltype7")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype7.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype7.html){target="_blank"}

```{r}
#| echo: false
#INRGWa
annot <- ("celltype6")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()

![](snapshots/celltype6.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype6.html){target="_blank"}

### Central brain interneurons

```{r}
#| echo: false
#INexsn
annot <- ("celltype188")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()
path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)
```

![](snapshots/celltype188.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype188.html){target="_blank"}

```{r}
#| echo: false
#INface
annot <- ("celltype193")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()
path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)
```

![](snapshots/celltype193.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype193.html){target="_blank"}

```{r}
#| echo: false
#INmidL
annot <- ("celltype118")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()
path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)
```

![](snapshots/celltype118.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype118.html){target="_blank"}

```{r}
#| echo: false
#INmus
annot <- ("celltype174")
plot_cell_name(annot, "Interneuron")
plot_cell_chars(annot, "Interneuron")
rgl <- plot_cell_rgl(annot, "Interneuron", "anterior")
widgets <- rglwidget(scene3d(rgl))
# make snapshot
path1 <- paste("_site/snapshots/", annot, ".png", sep = "")
rgl.snapshot(path1)
close3d()
path2 <- paste("_site/celltype_RGLs/", annot, ".html", sep = "")
htmlwidgets::saveWidget(widgets, path2)
```

![](snapshots/celltype174.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype174.html){target="_blank"}
